Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
minor

% why? why were these tasks selected? can we drop in the phrase ``multi-dimensional subjective choice task'' and refer back to PS.1 to justify the choice of tasks?
We based our two tasks on choosing a university and picking a restaurant for a large social event, because in PS.1 the majority of people stated that they had used multiple websites for these tasks.  We used different two different variables for both tasks, where the restaurant was located (Glasgow and Cambridge) and which subject people chose (sport science and history).  For the restaurant task, the cities Glasgow and Cambridge were chosen because they were geographically distant to participants, and would therefore minimise likelihood of prior familiarity with the restaurants or location.  For the University selection task, two university courses were selected at random from the complete university guide\footnote{The Complete University Guide:\\\url{www.thecompleteuniversityguide.co.uk}}, and the six top-ranked universities for each subject were selected as candidates.  
% \subsubsection{Task preparation} In order to prepare the data for our tasks, we identified websites that people commonly used for selecting universities and restaurants (see Table \ref{tab:studyfactors}).  Once we had compiled the list of websites, we select the top most used six for each task. 
We selected six because it enables us to scope our study, we found through two pilot studies that six data sources provided a sufficient challenge for users to explore the data and required them to use DP's main features. We manually collected the key data points from the websites for use in DP and into Excel spreadsheets (which 40\% of the participants in PS.1 said that had previously used to compare data).

>>>>

% why? why were these tasks selected? can we drop in the phrase ``multi-dimensional subjective choice task'' and refer back to PS.1 to justify the choice of tasks?
We based our two tasks on choosing a university and picking a restaurant for a large social event, because in PS.1 the majority of people stated that they had used multiple websites for these tasks.  We used two different variables for both tasks, where the restaurant was located (Glasgow and Cambridge) and which subject people chose (sport science and history).  For the restaurant task, the cities Glasgow and Cambridge were chosen because they were geographically distant to participants, and would therefore minimise likelihood of prior familiarity with the restaurants or location.  For the University selection task, two university courses were selected at random from the complete university guide\footnote{The Complete University Guide:\\\url{www.thecompleteuniversityguide.co.uk}}, and the six top-ranked universities for each subject were selected as candidates.  
% \subsubsection{Task preparation} In order to prepare the data for our tasks, we identified websites that people commonly used for selecting universities and restaurants (see Table \ref{tab:studyfactors}).  Once we had compiled the list of websites, we select the top most used six for each task. 
We selected six because it enables us to scope our study, we found through two pilot studies that six data sources provided a sufficient challenge for users to explore the data and required them to use DP's main features. We manually collected the key data points from the websites for use in DP and into Excel spreadsheets (which 40\% of the participants in PS.1 said that had previously used to compare data).
